State of the Practice for Lattice Boltzmann Method Software

### 2022-04-25 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Revisions to Section 4

To address \rqref{RQ_CompareHQ2Popular}, Table~\ref{repometrics} compares our
LBM software package rankings against their popularity in the research
community, as estimated by repository stars and watches. Nine packages do not
use GitHub, so they do not have a measure of repository stars. Looking at the
repository stars of the other 15 packages, we can observe a pattern where
packages that have been highly ranked by our assessment tend to have more stars
than lower ranked packages. Our best ranked package (ESPResSo) has the second
most stars, while our ninth ranked package (Sailfish) has the highest number of
stars. The repository watch column shows the same correlation, although
this column contains less data, since two of the packages (Palabos, waLBerla)
use GitLab, which does not track watches. Consistent with the star measure, our
ninth ranked package (Sailfish) has the highest number of watches and our best
ranked package (ESPResSo) has the second most watches. Packages designated as
lower quality often do not use GitHub or GitLab, or have only a few
stars and watches. Although the details of the rankings differ, our measures show
that following best practices tends to correlate with increased popularity in
the scientific community.

Notable exceptions to this trend occur for three projects that rank high by star
count, but relatively low in the ``follow best practices'' ranking: TCLB (star
rank 3, our rank 12), lettuce (star rank 4, our rank 14) and \esp{} (star rank
5, our rank 15).  Part of the discrepancy is because our process ranks all
projects, but the star measure does not apply to all projects.  Also, our
process equally weights all qualities (Section~\ref{Sec_OverallQuality}), but
for real users some qualities will be more important than others. Discrepancies
between our measures and the star measures may also be due to inaccuracy with
using stars to approximate popularity, because of how people use stars, because
young projects have less time to accumulate stars, and because stars represent
the community's feeling in the past more than current preferences
\citep{Szulik2017}. Older packages (like \esp{} and TCLB) have had more time to
accumulate stars and watches. Young projects have less time to accumulate stars,
like HemeLB, which only has 12 stars (at the time of measurement) having
recently moved from a different GitHub repository.  Lettuce is a young project
(released in 2019) with a relatively high number of stars. The discrepancy in
rankings may be due to a mismatch between the time we manually measured lettuce
and when we counted the stars. The late addition of Musubi meant a large gap
between when we measured projects and the time when our automated data (like
stars) was collected. A final reason for inconsistencies between our ranking and
the community's ranking is that, as for consumer products, more factors
influence popularity than just quality.

>>>>

To address \rqref{RQ_CompareHQ2Popular}, Table~\ref{repometrics} compares our
LBM software rankings against their popularity in the research community, as
estimated by repository stars and watches. Nine packages do not use GitHub, so
they do not have a measure of repository stars. Looking at the repository stars
of the other 15 packages, we observe a pattern where packages that have been
highly ranked by our assessment tend to have more stars than lower ranked
packages. Our best ranked package (ESPResSo) has the second most stars, while
our ninth ranked package (Sailfish) has the highest number of stars. The
repository watch column shows the same correlation, although this column
contains less data, since two of the packages (Palabos, waLBerla) use GitLab,
which does not track watches. Consistent with the star measure, our ninth ranked
package (Sailfish) has the highest number of watches and our best ranked package
(ESPResSo) has the second most watches. Packages designated as lower quality
often do not use GitHub or GitLab, or have only a few stars and watches.
Although the details of the rankings differ, our measures show that following
best practices tends to correlate with increased popularity in the scientific
community.

Notable exceptions to this trend occur for three projects that rank high by star
count, but relatively low in the ``follow best practices'' ranking: TCLB (star
rank 3, our rank 12), lettuce (star rank 4, our rank 14) and \esp{} (star rank
5, our rank 15).  Part of the discrepancy is because our process ranks all
projects, but the star measure does not apply to all projects.  Also, our
process equally weights all qualities (Section~\ref{Sec_OverallQuality}), but
for real users some qualities will be more important than others. Discrepancies
between our measures and the star measures may also be due to inaccuracy with
using stars to approximate popularity, because of how people use stars, because
young projects have less time to accumulate stars, and because stars represent
the community's feeling in the past more than current preferences
\citep{Szulik2017}. Older packages (like \esp{} and TCLB) have had more time to
accumulate stars and watches. Young projects have less time to accumulate stars,
like HemeLB, which only has 12 stars (at the time of measurement) having
recently moved from a different GitHub repository.  Lettuce is a young project
(released in 2019) with a relatively high number of stars. The discrepancy in
rankings may be due to a mismatch between the time we manually measured lettuce
and when we counted the stars. The late addition of Musubi means a gap between
when we measured projects and the time when our automated data (like stars) was
collected. A final reason for inconsistencies between our ranking and the
community's ranking is that, as for consumer products, more factors influence
popularity than just quality.
